Computer Science House Constitution

### 2025-06-09 constitution.tex

\asubsection{Semantic Changes}
\asubsubsection{Amendments}
Any semantic change to the Constitution requires the change to be proposed in writing for discussion at a House Meeting.
Any modifications made due to the discussion are added to the written proposal and the modified proposal is posted during the week.
The final proposal is presented the following week, and ballots are distributed for a Balloted Two-Thirds Vote with two-thirds quorum as described in \ref{Balloted Vote}.
The ballots are collected for a minimum of a forty-eight hour period.
A quorum of two-thirds of Eligible Votes must cast ballots for the vote to be official.
A vote equaling or exceeding two-thirds of the number of Votes Cast is required for the change to be placed into the Constitution.
\asubsubsection{Overrides}
The Constitution may be overridden by an Immediate Nine-Tenths Vote with eighty-five percent quorum as described in \ref{Immediate Vote}.

@@

\asubsection{Eligible Votes}
The number of Active Members eligible to vote on the issue.

>>>>

\asubsection{Semantic Changes}
\asubsubsection{Amendments}
Any semantic change to the Constitution requires the change to be proposed in writing for discussion at a House Meeting.
Any modifications made due to the discussion are added to the written proposal and the modified proposal is posted during the week.
The final proposal is presented the following week, and ballots are distributed for a Balloted Two-Thirds Vote with two-thirds quorum as described in \ref{Balloted Vote}.
The ballots are collected for a minimum of a forty-eight hour period.
A quorum of two-thirds of Eligible Votes must cast ballots for the vote to be official.
A vote equaling or exceeding two-thirds of the number of Votes Cast is required for the change to be placed into the Constitution.
\asubsubsection{Compliance with RIT Policy and New York State Law}
Any change made to Article  \ref{ADHERENCE TO UNIVERSITY POLICIES} which is made due to an update in NY law or RIT policy may be treated as a Non-Semantic change.

\asubsubsection{Overrides}
The Constitution may be overridden by an Immediate Nine-Tenths Vote with eighty-five percent quorum as described in \ref{Immediate Vote}.

@@

\asubsection{Eligible Votes}
The number of Active Members eligible to vote on the issue.
The eligible voters for a vote are determined and fixed when the Voting Period begins.
